---
title: How can the effectiveness of scare-off measure on wild boar be measured? 
subtitle: Semesterproject 022, Patterns and Trends in Environmental Data - Computational Movement Analysis
author: Mathujah Manikkan and Gioele Pinana
output: html_document

---


<!-- You can add  your R Code with Code chunks-->

```{r, echo = FALSE, warning=FALSE, message=FALSE}

# You can set chunk options individually per code chunk, as was done with this
# code chunk.

# echo = FALSE           hides the code from the generated output
# warning = FALSE        hides warnings from the generated output
# message = FALSE        hides messages from the generated output

# To set the setting for all code chunks, use the following code:

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```



```{r, echo = FALSE, warning=FALSE, message=FALSE}

library(ComputationalMovementAnalysisData)

head(wildschwein_BE)

```

## Abstract
Over the past few years, the population of wild boars in Switzerland has increased rapidly. As the number of wild boars increases, so does the damage to agriculture, as they seek for food in the fields. To counteract this damage, new preventive measures such as schreck, dogs, staged shots have been developed with the aim of preventing the wild boars from entering the fields. Within this semester project we want to measure the effectiveness of the scare-off measure schreck. 
-Data
Coordinates at 15-minute intervals of wild boars locations in the region of Fanel in the canton of Bern 
Coordinates of schreck-locations
Time intervals when the schreck-installations were on and off 
Landuse layer

  
-Development of two approaches to measure effectiveness and critical discussion of pros and cons.


## Introduction

<!-- the following is just a placeholder text, remove it!-->
Until 1945, only a few animals arrive in Switzerland from Germany, France and Italy. Between 1945 and 1952 more frequent wild boars were then recorded in Switzerland and the Principality of Liechtenstein. However, the population was not able to establish itself until between 1970 and 1990. Since 1990, the population of wild boars has been growing strongly, as evidenced by the number of animals shot and killed in traffic accidents. Possible reasons for the strong population increase are milder winters, an additional number of fattening years as well as the almost inexhaustible and mostly freely available food supply on agricultural land. Based on the planned realization of wildlife passages, it is assumed that the population will expand in the Central Plateau as well as in the Pre-Alps in the next few years. (Säugetieratlas, 2021)

Wild boars are omnivores and spend a large part of their time searching for food, covering an average of 5 km per night. Wild boars are mainly active during the night and as the only representative of the cloven-hoofed animals, they can reach food in the ground. To do this, it digs up the top layer of soil to a depth of 20-60 cm with its snout disc, which is ideally suited for this purpose. In the soil wild boars find large quantities of invertebrates and roots, but also mice, the nests and supplies. Wild boars also find a large part of their food on agricultural land. Particularly popular are corn, wheat and canola. Over the summer and in the fall wild boars eat fat, from which they can then feed over the meager winter months and also in the spring. Wild boars are very loyal to their location, but do not defend a territory. Thus, several herds can be on the move in the same area. Aggressive behavior between the rods occurs only when they occur at the same time at a food source. Depending on the region, the activity areas vary in size, with 2.5-12 km2 for males and 4.5-30 km2 for does. (Säugetieratlas, 2021)

Agricultural fields can be protected with prevention methods such as electric fencing clasping closures and acoustic reduction methods. In areas with high wild boar densities and near preferred roosting areas, such as water and migratory bird reserves, alternative crops attractive to wild boar should be used. This can not only prevent direct conflicts, but also indirectly limit accessible population growth. (Säugetieratlas, 2021)

```{r}
library(ComputationalMovementAnalysisData)
library(ggplot2)

# Include tables with the function "kable"

knitr::kable(head(wildschwein_BE))
```

<!-- the following is just a placeholder text, remove it!-->


```{r}
# include plots automatically



```




## Material and Methods
Within this semester project, two methods are analyzed in order to determine the effectiveness of the scare method and their strengths and weaknesses are compared. Before 

1. Method
The first approach analyzes the presence of wild boars by selected agricultural fields. Thereby, it is examined which wild boars were observed in the selected field before the activation of the scare and if and how often they were observed in the same field after the activation. Based on this analysis, a conclusion can be made by statistical analysis (P-value). 

2. Method
The second approach compares the mean distance between wild boar and schreck-locations, when turned on and when turned off. Therefore we measure a statistical effectiveness using p-value: 
*define relevant schreck-locations : the ones near the wild boar 
*choose 3 wild board to do the analysis
*calculate distances 
*t-Test and box-plot 





## Results

<!-- the following is just a placeholder text, remove it!-->
Philosophy oneself passion play fearful self noble zarathustra deceptions sexuality. Endless ocean of oneself dead ocean. Selfish decrepit.

## Discussion

<!-- the following is just a placeholder text, remove it!-->
Justice convictions spirit sexuality insofar free marvelous joy. Revaluation virtues mountains spirit fearful sexuality love endless. Society intentions will noble burying aversion moral. Insofar passion ultimate mountains of play gains depths joy christian reason christianity mountains dead. Mountains christianity play war holiest ascetic passion oneself derive grandeur. Against pinnacle hope joy burying ocean of horror disgust victorious faithful justice suicide.

